Diversification of Australian blind snakes

### 2022-11-03 manuscript.Rmd
prep for j of biogeography

---
title: "Diversification of Australian blind snakes"
date: "`r Sys.Date()`"
author: 
output: 
  # bookdown::html_document2:
  #   toc: true
  #   number_sections: FALSE
  bookdown::word_document2:
    reference_docx: [C:/Users/ST/Documents/repo/AusARG_blindsnake/custom-reference-doc.docx]
    number_sections: true
    fig_caption: yes
bibliography: [C:/Users/ST/Documents/repo/anu_thesis_texts/zotero_library.bib]
# biblio-style: "apalike"
csl: evolution.csl
link-citations: true
editor_options:
  chunk_output_type: console
---

@@

**Keywords**
scolecophidia, Diversification, paleoclimate, RPANDA, BioGeoBEARS

@@

<!-- Aridification  -->

The aridification on continental Australia over the past 20 million years resulted in a diversity of habitats and spurred multiple radiations of flora and fauna across the continent, many of which are endemic [@byrneBirth2008; @melvilleEvolutionary2011]. The arid zone makes up the majority of the Australian landscape and provides habitat to ~43% of all Australia’s terrestrial reptiles. Squamate reptiles (lizards and snakes) represent the largest vertebrate diversity in Australia with over 1000 species (~800 lizards and ~200 snakes), many of which have undergone rapid diversification in the last 10 – 6 myr [@brennanMass2017;@oliverPhylogenetic2017]. For example, some Australian squamate clades like dragons [@melvilleIntegrating2019], sphenomorphine skinks [@raboskyAnalysis2014], geckos [@ashmanDiversification2018;@brennanMass2017] and elapid snakes [@leeDiversification2016;@grundlerTrophic2014] show increased rates of diversification coincidentally with the onset of aridification. However, these studies did not account for heterogeneity of the arid zone [@pepperLife2021].

@@

We 
(1) evaluated the model fit performance of localised versus globalised temperature on the diversification of Australian blindsnake radiation, 
(2) compared the model fit between different ecological processes on diversification rates, and 
(3) reconstructed the ancestral biome of Australian blindsnakes? 
(4) Are there differences in the rates of speciation between arid and non-arid zones?

@@

@@

## Paleoclimate conditions

@@

- Range expansion was important for diversification ...
- Topography dyanmics [@brazModelling2021]

@@

- Solomon Island 40 MYA [@hallCenozoic2002]

## Arid vs. non-arid speciation

@@

>>>>

---
title: "Diversification of Australian blind snakes"
date: "`r Sys.Date()`"
author: 
output: 
  # bookdown::html_document2:
  #   toc: true
  #   number_sections: FALSE
  bookdown::word_document2:
    reference_docx: [C:/Users/ST/Documents/repo/AusARG_blindsnake/custom-reference-doc.docx]
    number_sections: true
    fig_caption: yes
bibliography: [C:/Users/ST/Documents/repo/anu_thesis_texts/zotero_library.bib]
# biblio-style: "apalike"
csl: jbiogeography.csl
link-citations: true
editor_options:
  chunk_output_type: console
---

@@

**Taxon**: Blind snakes

**Location**: Australasia

**Methods**:

**Results**:

**Main conclusions**:

**Keywords**
scolecophidia, Diversification, paleoclimate, BioGeoBEARS

@@

<!-- Aridification  -->
The aridification on continental Australia over the past 20 million years resulted in a diversity of habitats and spurred multiple radiations of flora and fauna across the continent, many of which are endemic [@byrneBirth2008; @melvilleEvolutionary2011]. The arid zone makes up the majority of the Australian landscape and provides habitat to ~43% of all Australia’s terrestrial reptiles. Squamate reptiles (lizards and snakes) represent the largest vertebrate diversity in Australia with over 1000 species (~800 lizards and ~200 snakes), many of which have undergone rapid diversification in the last 10 – 6 myr [@brennanMass2017;@oliverPhylogenetic2017]. For example, some Australian squamate clades like dragons [@melvilleIntegrating2019], sphenomorphine skinks [@raboskyAnalysis2014], geckos [@ashmanDiversification2018;@brennanMass2017] and elapid snakes [@leeDiversification2016;@grundlerTrophic2014] show increased rates of diversification coincidentally with the onset of aridification. However, these studies did not account for heterogeneity of the arid zone [@pepperLife2021].

@@

We 
(1) evaluated the model fit performance of localised versus globalised temperature on the diversification of Australian blindsnake radiation, 
(2) compared the model fit between different ecological processes on diversification rates, and 
(3) reconstructed the ancestral biome of Australian blindsnakes? 
(4) reconstructed ancestral niche and model niche evolution of the radiation
(5) Are there differences in the rates of speciation between arid and non-arid zones?

@@

## Niche evolution

We reconstructed ancestral niche from present-only data using NEMo package.

@@

## Paleoclimate estimates

@@

- Range expansion was important for diversification ...
- Topography dyanmics [@brazModelling2021]
- Solomon Island 40 MYA [@hallCenozoic2002]

@@

Rates of diversification between arid and non-arid, and widespread.

## Niche evolution

@@

## Niche evolution
